### 2019-08-27 paper_03_toy_model/article.tex

Comparing the spectral energy fluxes from a full GCM shown in Fig.~\ref{Flux} with the corresponding fluxes in Fig.~\ref{F2} from run 3 of the toy model we see that there is a striking similarity. A considerable amount of APE which is forced at large scales is converted into KE. A part of the KE is going into a downscale cascade at $ k > k_f $, while the other part, which is of the same order of magnitude, is going into an upscale cascade at $ k < k_f $. The upscale cascade is restricted to KE and is produced by interactions only involving the rotational component of the velocity field. The downscale energy cascade, on the other hand, is a cascade of both APE and KE. Here we also see an important difference. In the toy model there is perfect equipartition between KE and APE at high wave numbers and also between the fluxes $ \Pi_K $ and $ \Pi_A $. In the GCM, on the other hand, $ \Pi_K > \Pi_A $ at corresponding wave numbers. Clearly, the downscale energy cascade in the GCM is not a clean wave energy cascade with equipartition between KE and APE. \citet{Callies-Ferrari-Buhler:2014} have suggested that the mesoscale $ k^{-5/3} $ spectrum is produced by inertia-gravity waves with frequencies that are close to $ f $. For such waves, $ E_K > E_A $. However, the kinetic energy content in the rotational component of the velocity field is necessarily smaller than in the divergent component, and that is at odds with observational evidence \citep{Lindborg:2015, QiangLi2017}.  There is also numerical evidence \citep{Deusebio-Vallgren-Lindborg:2013, Asselin2017} suggesting that the forward energy mesoscale energy cascade cannot be described as a cascade of waves at high wave numbers, although it may start as a wave cascade at low wave numbers. In any case, as we pointed out earlier, the forward energy cascade in the GCM cannot be produced by inertia-gravity waves with frequencies close to $ f $, since it would require much finer resolution in the vertical to simulate such motions. Neither can it be fully accounted for by stratified turbulence as suggested by \citet{Lindborg2006}, since that would also require much finer resolution. In the toy model simulation, on the other hand, we have been able to simulate a downscale energy cascade using only a single level. All nonlinear interactions that are present in the toy-model are also present in the dynamical equations of a full GCM, at each level. Moreover, in the GCM both $ E_A $   and $ E_K $ can be expressed as quadratic quantities to lowest order and the  sum of $ E_A $ and $ E_K $ is approximately conserved. Therefore, it seems likely that the toy model catches the essential cascade dynamics of the GCM. An important difference is, of course, that  inertia-gravity waves in the full GCM, as well as in nature, are three-dimensional, anisotropic and much more dispersive than in the toy model.

>>>>

Comparing the spectral energy fluxes from a full GCM shown in Fig.~\ref{Flux} with the corresponding fluxes in Fig.~\ref{F2} from run 3 of the toy model we see that there is a striking similarity. A considerable amount of APE which is forced at large scales is converted into KE. A part of the KE is going into a downscale cascade at $ k > k_f $, while the other part, which is of the same order of magnitude, is going into an upscale cascade at $ k < k_f $. The upscale cascade is restricted to KE and is produced by interactions only involving the rotational component of the velocity field. The downscale energy cascade, on the other hand, is a cascade of both APE and KE. Here we also see an important difference. In the toy model there is perfect equipartition between KE and APE at high wave numbers and also between the fluxes $ \Pi_K $ and $ \Pi_A $. In the GCM, on the other hand, $ \Pi_K > \Pi_A $ at corresponding wave numbers. Clearly, the downscale energy cascade in the GCM is not a clean wave energy cascade with equipartition between KE and APE. \citet{Callies-Ferrari-Buhler:2014} have suggested that the mesoscale $ k^{-5/3} $ spectrum is produced by inertia-gravity waves with frequencies that are close to $ f $. For such waves, $ E_K > E_A $. However, the kinetic energy content in the rotational component of the velocity field is necessarily smaller than in the divergent component, and that is at odds with observational evidence \citep{Lindborg:2015, LiLindborg2018}.  There is also numerical evidence \citep{Deusebio-Vallgren-Lindborg:2013, Asselin2017} suggesting that the forward energy mesoscale energy cascade cannot be described as a cascade of waves at high wave numbers, although it may start as a wave cascade at low wave numbers. In any case, as we pointed out earlier, the forward energy cascade in the GCM cannot be produced by inertia-gravity waves with frequencies close to $ f $, since it would require much finer resolution in the vertical to simulate such motions. Neither can it be fully accounted for by stratified turbulence as suggested by \citet{Lindborg2006}, since that would also require much finer resolution. In the toy model simulation, on the other hand, we have been able to simulate a downscale energy cascade using only a single level. All nonlinear interactions that are present in the toy-model are also present in the dynamical equations of a full GCM, at each level. Moreover, in the GCM both $ E_A $   and $ E_K $ can be expressed as quadratic quantities to lowest order and the  sum of $ E_A $ and $ E_K $ is approximately conserved. Therefore, it seems likely that the toy model catches the essential cascade dynamics of the GCM. An important difference is, of course, that  inertia-gravity waves in the full GCM, as well as in nature, are three-dimensional, anisotropic and much more dispersive than in the toy model.
